Revealing transient strain in geodetic data with Gaussian process regression

### 2017-10-23 RevisedSubmission/hines_hetland_2017_gji.tex
did more

We provide an example to give the covariance function for $u_i$ a more
tangible meaning. we can use a squared exponential function for $X_i$
and $T_i$,

@@

\begin{figure*}
\includegraphics{figures/prior_demo/prior-demo.pdf}
\caption{ 
Panel A) The covariance function $C_{u_i}$ using a squared exponential
to describe the spatial and temporal covariance of $u_i$ (eq.
\ref{eq:ExampleCov}). Panel B) A single realization of $u_i$ using the
covariance function from Panel A. The realization is really a function
of three variables, $t$, $x_\mathrm{e}$, and $x_\mathrm{n}$, although
we only show its dependence on $t$ and one of the spatial dimensions.
}    
\label{fig:PriorDemo}
\end{figure*}

>>>>

We provide an example to give the prior on transient displacements a
more tangible meaning. we can use a squared exponential function for
$X_i$ and $T_i$,

@@

\begin{figure*}
\includegraphics{figures/prior_demo/prior-demo.pdf}
\caption{ 
Panel A) The covariance between $u_i(p)$ and $u_i(p')$,
$C_{u_i}(p,p')$, as a function of the spatial and temporal distance
between $p$ and $p'$. The covariance function $C_{u_i}$ is composed of
squared exponentials to describe the spatial and temporal covariance
of $u_i$ (eq. \ref{eq:ExampleCov}). Panel B) A single realization of
$u_i$ using the covariance function from Panel A. The realization is
really a function of three variables, $t$, $x_\mathrm{e}$, and
$x_\mathrm{n}$, although we only show its dependence on $t$ and one of
the spatial dimensions.
}    
\label{fig:PriorDemo}
\end{figure*}
